|

### 2019-08-29 paper.Rmd
Working on the introduction

<!-- The disadvantage of projection: opacity, occlusion, even with pseudo-transparency from scatterplots;  motivation -->
Additionaly, we may complement projections with section information. This is often possible in interactive graphics systems by means of brushing [@ggobiCSDA2003;@JSSv081i05], where the user is selecting a region in a subspace of the dataspace that is highlighted in a projection of the data points.

<!-- Our approach: introduce sections; many different ways to slice, refer to linked brushing as slicing whcih mirrors prosection, but here we will explain/utilise a simple slicing on the projection where point in orthogonal space are faded. -->
The complementarity between projections and sections has previously been discussed in @prosection, dubbing the combination "prosections". These prosections allow the identification of lower-dimensional structure embedded in the high-dimensional space. One simple example is that prosections can reveal the difference between a full and hollow hypersphere. In addition to hollowness (concave structures) they can also provide a clear picture of internal structures that may be concealed in a projection. For example, @prosection uses prosections to reveal the internal structure of the four-point ultrametric locus [@locus]. Since existing approaches to sectioning are interactive, they rely on the user to redefine the section many times to explore the data. While this level of control is often preferred, it is impractical for detecting and exploring unknown structures in a dataset. As a result smaller hidden features that are only visible in specific sections of the full distribution may easily be missed. In addition having a dynamic approach to sectioning, similar to the grand tour approach to projections, will provide the viewer with context allowing to extrapolate e.g. the shape of a concave structure. We therefore propose a more systematic approach to sectioning based on interpolated projections obtained with a grand tour. The method defines a slice based on 2-d projections provided by the tour and will presents the viewer with an interpolated sequence of slices when running a tour.

<!-- paper structure --> 
The relevant definitions and an overview of the implementation in R are given in Section XXX, and in Section XXX. We then apply the newly defined slice tour to several examples in Section XXX. We consider different high-dimensional geometric shapes and XXX, showing how concave structures can be visualised and explored with a slice tour. Possible extensions are discussed in Section XXX.

<!--
A good way to visualize high-dimensional data is to display a smooth sequence of interpolated lower dimensional projections. This is called a tour [@As85; @BCAH05] and allows to extrapolate the high-dimensional shape of the distribution. It is particularly useful for detecting clusters, outliers and non-linear dependence. A limitation of this approach is that concavities in a distribution may be hidden when looking at projections. A simple example are projections of samples on a hypersphere. No projection of such a distribution allows to distinguish a hollow sphere from a full one. On the other hand, the difference would be obvious when looking at a slice through the center of the sphere.

Slicing or sectioning can be thought of as complementary to projections when visualizing high-dimensional data, as discussed in detail in @prosection. To overcome the respective shortcomings of each method, it is suggested to use a composition of sections and projections, so-called "prosections". In practice sectioning is typically performed in interactive graphics displays in the form of brushing [XXX reference?], i.e. the user is selecting a region in a subspace of the high-dimensional dataspace that is highlighted in a projection of the data points.
More recently @JSSv081i05 suggested conditional visualization for statistical models by selecting sections in data space for detailed comparisons of a fitted model to the observed data. Similar to brushing, the section is selected interactively by the user, by choosing a point in low-dimensional displays showing the data in the space of conditioning predictors.

Here we propose a systematic approach to slicing that does not rely on the user choosing sections to display, but will present the viewer with an interpolated sequence showing different slices of parameter space. The method is based on the grand tour, and uses the orthogonal distance from the current plane to define the section corresponding to each view in an interpolated tour path. We demonstrate how this can be used to gain insights into the concave structure of a dataset, using the example of hollow hyperspheres defined in 3 or more dimensions.
-->

>>>>

<!-- The disadvantage of projection: opacity, occlusion, even with pseudo-transparency from scatterplots;  motivation -->
A major limitation of projections is their opacity, even if mitigated somewhat through the pseudo-transparancy present in sparse scatterplots. As a result certain features of distributions may easily be hidden in projections, especially in the case of concave structures. Considering the example of a simple geometric shape such as a hypershere, we understand that projections cannot distinguish between a full or a hollow sphere. Similarly we can think of small scale structures hidden in the center of a multivariate distribution. Again projections will not help in findig such features in a distribution. Other examples where the use of projections is limited include the visualisation of non-linear boundaries between groups, that will be obscured in each projection.

<!-- Our approach: introduce sections; many different ways to slice, refer to linked brushing as slicing whcih mirrors prosection, but here we will explain/utilise a simple slicing on the projection where point in orthogonal space are faded. -->
We can overcome these limitations when adding section information, see e.g. @prosection. For our example of the hypersphere, we can clearely identify a hollow sphere when looking at a slice throught the distribution, where all points will lie on a circle in a 2d slice. In practice there are many different ways to slice, typically facilitated through linked brushing (e.g. @ggobiCSDA2003, @JSSv081i05), where the user is selecting a region in a subspace of the dataspace that is highlighted in a projection of the data points. These systems are interactive, and rely on the user to redefine the section many times to fully explore the data in this way. In this note we introduce a simple slicing method for projections where points in the orthogonal space are faded. Combining it with the grand tour results in a new dynamic display that can be used to systematically search for features hidden in sections.

<!-- paper structure --> 
The method and its implementation in R are described in Section XXX, and in Section XXX. We then apply it to several examples in Section XXX. We consider different high-dimensional geometric shapes and XXX, showing how concave or occluded structures can be visualised and explored with a slice tour. Possible extensions are discussed in Section XXX.
